Measuring and optimizing machine learning interpretability

### 2019-06-27 2019-reisensburg/2019-reisensburg-molnar.Rmd
finishes version of reisensburg talk

TODO: Image of 3 vs 100 feature in importance

@@

TODO: Image from paper with PDP and increasing interactions

@@

TODO: Image with increasing MEC

>>>>

```{r, echo=FALSE, out.width = '\\textwidth'} 
knitr::include_graphics("../images/pdp-multiple.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("../images/pdp-interactions.jpeg")
```

@@

```{r}
set.seed(2)
x = seq(from = -1, to = 1, length.out = 50)
y1 = x
y2 = x * (x < 0.3) + 0.4 * (x > 0.3)
y3 = x + sin(8 * x) 
y3 = y2 + cumsum(rt(50, df = 1)) / 50 - 1

dat = data.frame(x = rep(x, times = 3), y = c(y1, y2, y3), situation = rep(c(1,2,3), each = 50))
library(ggplot2)
ggplot(dat) + geom_line(aes(x = x, y = y)) + facet_grid(. ~ situation)
